\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-20 pldi/draft.tex
Add tiled table

\begin{figure*}[t]
    \centering
    %% \subcaptionbox{\label{eval:minimal_grep}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:grep}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/grep_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:minimal_sort}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:topn}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:wf}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:spell}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
    %% }
    %% \caption{a}
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_grep}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/spell_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:grep}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
      \centering
      \includegraphics[width=\textwidth]{\detokenize{./figs/set-diff_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%

    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:topn}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:wf}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/shortest_scripts_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:spell}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
      \centering
      \includegraphics[width=\textwidth]{\detokenize{./figs/bigrams_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%
    \caption{
      \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
      Four different configurations per benchmark:
      (i) \todo{Par + Split}, showing the performance of \sys with both eager and split optimizations enabled,
      (ii) \todo{Par + B. Split}, showing the performance of \sys with eager and the \todo{batch-size annotated} split optimizations enabled,
      (ii) \todo{Parallel}, showing the performance of \sys with eager enabled and split disabled,
      (iii) \todo{No Eager}, showing the performance of \sys with split and eager disabled,
      (iv) \todo{Blocking Eager}, showing the performance of \sys with split disabled and the naive blocking eager enabled,
      \nv{Maybe it makes sense to show log x-axis?}
      \kk{How can we also fit two more plots (sort-sort and diff) here? Maybe we can fit one by getting rid of sort (since it also shown in the sort--parallel one). Otherwise we could separate the ``split'' plots from the ones that don't have split.}
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \caption{
      \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
      Four different configurations per benchmark:
      (i) \todo{Par + Split}, showing the performance of \sys with both eager and split optimizations enabled,
      (ii) \todo{Par + B. Split}, showing the performance of \sys with eager and the \todo{batch-size annotated} split optimizations enabled,
      (iii) \todo{Parallel}, showing the performance of \sys with eager enabled and split disabled,
      (iv) \todo{No Eager}, showing the performance of \sys with split and eager disabled,
      (v) \todo{Blocking Eager}, showing the performance of \sys with split disabled and the naive blocking eager enabled,
      (vi) \todo{Opt. Parallel}, showing the performance of an optimized version of \ttt{bigrams}.
      \nv{Maybe it makes sense to show log x-axis?}
      \kk{How can we also fit two more plots (sort-sort and diff) here? Maybe we can fit one by getting rid of sort (since it also shown in the sort--parallel one). Otherwise we could separate the ``split'' plots from the ones that don't have split.}
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

%% \begin{figure*}[t]
%%     \centering
%%     %% \subcaptionbox{\label{eval:minimal_grep}}{
%%     %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
%%     %% }
%%     %% \subcaptionbox{\label{eval:grep}}{
%%     %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/grep_throughput_scaleup.pdf}}
%%     %% }
%%     %% \subcaptionbox{\label{eval:minimal_sort}}{
%%     %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
%%     %% }
%%     %% \subcaptionbox{\label{eval:topn}}{
%%     %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
%%     %% }
%%     %% \subcaptionbox{\label{eval:wf}}{
%%     %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
%%     %% }
%%     %% \subcaptionbox{\label{eval:spell}}{
%%     %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
%%     %% }
%%     %% \caption{a}
%%     \begin{subfigure}[b]{0.24\textwidth}
%%         \centering
%%         \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:minimal_grep}
%%     \end{subfigure}%
%%     ~
%%     \begin{subfigure}[b]{0.24\textwidth}
%%         \centering
%%         \includegraphics[width=\textwidth]{\detokenize{./figs/spell_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:grep}
%%     \end{subfigure}%
%%     ~
%%     \begin{subfigure}[b]{0.24\textwidth}
%%         \centering
%%         \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:minimal_sort}
%%     \end{subfigure}%
%%     ~
%%     \begin{subfigure}[b]{0.24\textwidth}
%%       \centering
%%       \includegraphics[width=\textwidth]{\detokenize{./figs/set-diff_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:minimal_sort}
%%     \end{subfigure}%

%%     \begin{subfigure}[b]{0.24\textwidth}
%%         \centering
%%         \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:topn}
%%     \end{subfigure}%
%%     ~
%%     \begin{subfigure}[b]{0.24\textwidth}
%%         \centering
%%         \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:wf}
%%     \end{subfigure}%
%%     ~
%%     \begin{subfigure}[b]{0.24\textwidth}
%%         \centering
%%         \includegraphics[width=\textwidth]{\detokenize{./figs/shortest_scripts_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:spell}
%%     \end{subfigure}%
%%     ~
%%     \begin{subfigure}[b]{0.24\textwidth}
%%       \centering
%%       \includegraphics[width=\textwidth]{\detokenize{./figs/bigrams_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:minimal_sort}
%%     \end{subfigure}%
%%     \caption{
%%       \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
%%       Four different configurations per benchmark:
%%       (i) \todo{Par + Split}, showing the performance of \sys with both eager and split optimizations enabled,
%%       (ii) \todo{Par + B. Split}, showing the performance of \sys with eager and the \todo{batch-size annotated} split optimizations enabled,
%%       (ii) \todo{Parallel}, showing the performance of \sys with eager enabled and split disabled,
%%       (iii) \todo{No Eager}, showing the performance of \sys with split and eager disabled,
%%       (iv) \todo{Blocking Eager}, showing the performance of \sys with split disabled and the naive blocking eager enabled,
%%       \nv{Maybe it makes sense to show log x-axis?}
%%       \kk{How can we also fit two more plots (sort-sort and diff) here? Maybe we can fit one by getting rid of sort (since it also shown in the sort--parallel one). Otherwise we could separate the ``split'' plots from the ones that don't have split.}
%%     }
%%     \vspace{-15pt}
%%     \label{fig:microbenchmarks}
%% \end{figure*}
